resevol: an R package for spatially explicit models of pesticide resistance

### 2022-11-24 notebook/ms/ms.Rmd
Add in a quick new paragraph in the manuscript to address comments from @MattTinsleyStirling and resolve Issue #47

Landscapes are spatially explicit and initialised in one of two ways. 
First, a landscape can be built from the arguments `xdim`, `ydim`, and `farms`. 
These arguments specify the dimensions of the landscape and the number of farms on it.
Contiguous rectangular farms of roughly equal size are generated on the landscape using a splitline algorithm.
Second, a custom landscape can be input using the `terrain` argument, which takes a matrix with elements that include integers 1 to `farms`.
Each value defines a unique farm, but values do not need to be contiguous.
These 'farms' could even model non-farmland (e.g., water, roads), if pesticides and crops on them are invisible to pests (see Supporting Information 2).
This `terrain` customisation therefore allows for a high degree of landscape detail, and offers the potential for modelling real-world landscapes from raster images.
Edge effects are set using the `land_edge` argument.
Edge options include `"leaky"` (pests disappear from the landscape), `"reflect"` (pests bounce off of the edge), `"sticky"` (pests stick to the edge), or `"torus"` (pests that move off of one edge return on the opposite side of the landscape).

Each farm can hold one pesticide and one crop type in any time step.
The `crop_init` and `pesticide_init` arguments initialise one of `crop_number` crops and one of `pesticide_number` pesticides for each farm, respectively (maximum of 10 each).
Initialisation can be random for each farm with equal probability, or it can be set using a vector of length `farms` in which vector elements define the initialised crop or pesticide number.
After initialisation, crops and pesticides rotate once every `crop_rotation_time` and `pesticide_rotation_time` time steps, respectively.
Each of these rotation time arguments can take either an integer value from 1-3, or a matrix.
Integer values specify (1) no rotation, (2) random transition from one type to another, or (3) cycling through each available crop or pesticide in numeric order.
Square matrices can be used to define the probability that a given crop or pesticide in row $i$ transitions to that in column $j$. 
Hence, any possible Markov chain can be used to model transition between crop or pesticide types on farms.

>>>>

Landscapes are spatially explicit and initialised in one of two ways. 
First, a landscape can be built from the arguments `xdim`, `ydim`, and `farms`. 
These arguments specify the cell dimensions and number of farms on the landscape.
Contiguous rectangular farms of roughly equal size are generated on the landscape using a splitline algorithm.
Second, a custom landscape can be input using the `terrain` argument, which takes a matrix with elements that include integers 1 to `farms`.
Each value defines a unique farm, but values do not need to be contiguous.
These 'farms' could even model non-farmland (e.g., water, roads), if pesticides and crops on them are invisible to pests (see Supporting Information 2).
This `terrain` customisation therefore allows for a high degree of landscape detail, and offers the potential for modelling real-world landscapes from raster images.
Edge effects are set using the `land_edge` argument.
Edge options include `"leaky"` (pests disappear from the landscape), `"reflect"` (pests bounce off of the edge), `"sticky"` (pests stick to the edge), or `"torus"` (pests that move off of one edge return on the opposite side of the landscape).

Each farm can hold one pesticide and one crop type in any time step.
The `crop_init` and `pesticide_init` arguments initialise one of `crop_number` crops and one of `pesticide_number` pesticides for each farm, respectively (maximum of 10 each).
Initialisation can be random for each farm with equal probability, or it can be set using a vector of length `farms` in which vector elements define the initialised crop or pesticide number.
After initialisation, crops and pesticides rotate once every `crop_rotation_time` and `pesticide_rotation_time` time steps, respectively.
Each of these rotation time arguments can take either an integer value from 1-3, or a matrix.
Integer values specify (1) no rotation, (2) random transition from one type to another, or (3) cycling through each available crop or pesticide in numeric order.
Square matrices can be used to define the probability that a given crop or pesticide in row $i$ transitions to that in column $j$. 
Hence, any possible Markov chain can be used to model transition between crop or pesticide types on farms.
Upon rotation, crop and pesticide values are reset on each farm.

Values for `crop_per_cell` and `pesticide_per_cell` determine the quantity of crops and pesticides initialised per cell upon crop or pesticide rotation, respectively.
Between crop rotations, crop values can increase each time step by a proportion or increment `crop_growth`, which depends on `crop_growth_type`.
These arguments can be used to model crop growth over a season.
